Measuring Political Freedom Around the World

### 2020-11-11 slides.Rmd
resized table

<font size="-10">
```{r results='asis'}
stargazer::stargazer(fit_df6, model_df5, fit_df4, type = "html", 
                     title = "Regression Results", 
                     covariate.labels = c(),
                     header = FALSE,
                     single.row = FALSE)
```

>>>>

<font size="2">
```{r results='asis'}
stargazer::stargazer(fit_df6, model_df5, fit_df4, type = "html", 
                     title = "Regression Results", 
                     covariate.labels = c(),
                     header = FALSE,
                     single.row = TRUE)
```
